rejected_text

### 2024-10-08 paper/rejected-text.qmd
Draft for full team review

>>>>

<!-- Describing @fig-Fig9, the most valuable variable for splitting the data was the proportion of single family households and % of LICO prevalence in the DA. The the terminal nodes represented as bar columns depict the percentage composition by supercluster. For the bar on the right, the majority of the parcels are F superclusters. Following the tree diagram, these F superclusters are described by having less than 15.8% single parent families (this is below the median of `r df_DA$One_parent_families |> median(na.rm=T) |> scales::percent()`). The bar on the left is mostly composed of parcels that are labeled A+. These A+ parcels are located in DAs greater than 15.8% single parent families and % LICO prevalence of 6.5% and greater (this is above the median of `r df_DA$LICO |> median(na.rm=T) |> round() |> paste0("%")`). In sum: residences in parcels with exceptionally complete and caring access tend to be lower-income and single-parent families, while residences in parcels with not caring are not complete access tend to have a lower presence of single parent households. Households with a higher proportion of single-family households (15.8% and greater) where LICO is lower have a mixed label membership (bar column in @fig-Fig9).  -->
